### 2018-11-07 Docs/FAQ/faq.tex

   The environment variable {\tt AMREX\_HOME} needs to be the full path
   to the {\tt amrex/} directory.  You cannot use `{\tt $\sim$}' as a shortcut
   for your home directory.

@@

\amrex\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  See \S
\ref{ch:makefiles:special}.

>>>>

   The environment variable {\tt FBOXLIB\_HOME} needs to be the full path
   to the {\tt FBoxLib/} directory.  You cannot use `{\tt $\sim$}' as a shortcut
   for your home directory.

@@

\fboxlib\ can intercept floating point exceptions and provide a helpful
backtrace that shows you where they were generated.  See \S
\ref{ch:makefiles:special}.

### 2018-11-07 Docs/MESA/hopper_compile.tex

These notes are somewhat dated because they pertain only to {\sf MESA} version 
4088. The above notes are for version 4411. In my experience, version 4088 is 
much easier to install than 4411. When using the scripts in 
{\sf AstroDev/MESA/networks/scripts}, make sure the proper list of modules to 
compile (lines containing {\tt do\_one ....}) is used. Those lists are 
version dependant.

Once {\sf MESA} was installed and working properly on a local machine (e.g. 
Bender), I tried installing it on Hopper, which is a Cray XE6 machine. On 
Bender, which is an Intel(R) Xeon(R) X5650 machine, the compiler was 
{\tt gcc} version 4.7.0, on Hopper I tried compiling {\sf MESA} with the 
Cray Compiler using version 8.0.5. The module that was loaded to enable this 
was {\tt PrgEnv-cray}.

There are several steps needed to compile {\sf MAESTRO} with {\sf MESA} on 
Hopper:
\begin{enumerate}
\item Download the {\tt MESA} source code using the command described in 
Section \ref{sec:setupmesa}
\item Edit the {\tt makefile\_header} in the {\tt utils} directory
\item Edit the {\tt build\_and\_test} script in the {\tt utils} directory
\item Edit the {\tt chem\_lib.f} file in the {\tt chem} directory
\item Edit the {\tt mtx} makefile
\item Edit the makefiles in {\tt screen}, {\tt utils}, {\tt num} and 
{\tt interp\_1d}
\item Edit the {\tt install} script in the main {\sf MESA} directory
\item Edit the {\tt BoxLib/Tools/F\_mk/GMakedefs.mak} makefile
\item Edit the {\tt BoxLib/Tools/F\_mk/comps/Linux\_cray.mak} file
\item Install {\sf MESA}
\item Compile {\sf MAESTRO}
\end{enumerate}

@@

When creating the library for these four modules, there is a {\tt LIB\_DEFS} 
variable in the makefile that holds the {\tt *\_def.o} file, e.g. 
{\tt utils\_def.o} or {\tt num\_def.o}. This file is never loaded into the 
library as seen below for the {\tt utils} directory. Certain modules have a 
{\tt *\_def.f} file with both definitions and declarations of data that will 
be needed at runtime, so they must be included in the library. Other modules 
have a {\tt *\_def.f} file that contains only definitions and no data 
declarations and therefor only needs to be included at compile time. The Cray 
compiler on Hopper for whatever reason complained that there were undefined 
references to certain {\tt *\_def.o} files. The undefined references only 
occurred for modules whose {\tt *\_def.f} file did not need to be included in 
the library. The fix was to manually include the {\tt *\_def.o} file in the 
library for all of the necessary module directories. The {\tt utils} directory 
is shown here:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\sf BoxLib Linux\_cray.mak} file}

@@

  cp make/libconst.a ../lib
  cd ../lib
  ranlib libconst.a
\end{lstlisting}
If the {\tt -ef} flag is not enabled, the {\tt .mod} file will be 
{\tt CONST\_LIB.mod} and will not get copied to the {\tt include} directory 
(the library is unaffected). The default for {\sf MAESTRO} is to not use 
the {\tt -ef} flag, but it does use the {\tt -em} flag. To make {\sf MAESTRO} 
and {\sf MESA} compatible, I added the {\tt -ef} flag to the 
{\tt Linux\_cray.mak} file located in {\tt BoxLib/Tools/F\_mk/comps}. I also 
added a few more debugging flags:
\begin{lstlisting}[language=make,mathescape=false]
  FFLAGS   += -J $(mdir) -I $(mdir) -emf
  F90FLAGS += -J $(mdir) -I $(mdir) -emf

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\sf BoxLib GMakedefs.mak} makefile}

In {\sf MAESTRO}, {\tt .mod} files are located in the {\tt \$(tdir)/m} 
directory, where {\tt tdir = t/\$(suf)} and {\tt \$(suf)} was in this case 
{\tt Linux.Cray}. This means the {\sf MAESTRO} routines are expecting to find 
module files with the name {\tt t/Linux.Cray/m/network.mod}. The addition of 
the {\tt -ef} flag affects the entire name of the module so the Cray compiler 
was creating files with the name {\tt t/linux.cray/m/network.mod}. To solve 
this, I modified what {\tt tdir} is defined to be when using the Cray compiler. 
This was done in the {\tt BoxLib/Tools/F\_mk/GMakedefs.mak} makefile by using 
a simple if statement:
\begin{lstlisting}[language=make,mathescape=false]
  ifeq ($(COMP), Cray)
    tdir = t/$(shell echo $(suf) | tr A-Z a-z)
  else
    tdir = t/$(suf)
  endif
  odir = $(tdir)/o
  mdir = $(tdir)/m
\end{lstlisting}
The shell command {\tt echo \$(suf) | tr A-Z a-z} has the effect of converting 
{\tt \$(suf)} to lowercase.

>>>>

These notes are somewhat dated because they pertain only to {\sf MESA} version 
4088. In my experience, version 4088 is 
very easy to install and follows the same steps as outlined above. When using 
the scripts in 
{\sf AstroDev/MESA/networks/scripts}, make sure the proper list of modules to 
compile (lines containing {\tt do\_one ....}) is used. Those lists are 
version dependant.

Once {\sf MESA} was installed and working properly on a local machine (e.g.\ 
Bender), I tried installing it on Hopper, which is a Cray XE6 machine. On 
Bender, which is an Intel(R) Xeon(R) X5650 machine, the compiler was 
{\tt gcc} version 4.7.0, on Hopper I tried compiling {\sf MESA} with the 
Cray Compiler using version 8.0.5. The module that was loaded to enable this 
was {\tt PrgEnv-cray}.

There are several steps needed to compile {\sf MAESTRO} with {\sf MESA} on 
Hopper:
\begin{enumerate}
\item Download the {\tt MESA} source code (Section \ref{sec:setupmesa}) and 
be sure to use the correct version: {\tt svn co -r 4088 ...}
\item Edit the {\tt makefile\_header} in the {\tt utils} directory
\item Edit the {\tt build\_and\_test} script in the {\tt utils} directory
\item Edit the {\tt chem\_lib.f} file in the {\tt chem} directory
\item Edit the {\tt mtx} makefile
\item Edit the makefiles in {\tt screen}, {\tt utils}, {\tt num} and 
{\tt interp\_1d}
\item Edit the {\tt install} script in the main {\sf MESA} directory
\item Edit the {\tt amrex/Tools/F\_mk/GMakedefs.mak} makefile
\item Edit the {\tt amrex/Tools/F\_mk/comps/Linux\_cray.mak} file
\item Install {\sf MESA}
\item Compile {\sf MAESTRO}
\end{enumerate}

@@

When creating the library for these four modules, there is a {\tt LIB\_DEFS} 
variable in the makefile that holds the {\tt *\_def.o} file, e.g.\ 
{\tt utils\_def.o} or {\tt num\_def.o}. This file is never loaded into the 
library as seen below for the {\tt utils} directory. Certain modules have a 
{\tt *\_def.f} file with both definitions and declarations of data that will 
be needed at runtime, so they must be included in the library. Other modules 
have a {\tt *\_def.f} file that contains only definitions and no data 
declarations and therefor only needs to be included at compile time. The Cray 
compiler on Hopper for whatever reason complained that there were undefined 
references to certain {\tt *\_def.o} files. The undefined references only 
occurred for modules whose {\tt *\_def.f} file did not need to be included in 
the library. The fix was to manually include the {\tt *\_def.o} file in the 
library for all of the necessary module directories. The {\tt utils} directory 
is shown here:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\sf AMReX Linux\_cray.mak} file}

@@

  cp make/libconst.a ../lib
  cd ../lib
  ranlib libconst.a
\end{lstlisting}
If the {\tt -ef} flag is not enabled, the {\tt .mod} file will be 
{\tt CONST\_LIB.mod} and will not get copied to the {\tt include} directory 
(the library is unaffected). The default for {\sf MAESTRO} is to not use 
the {\tt -ef} flag, but it does use the {\tt -em} flag. To make {\sf MAESTRO} 
and {\sf MESA} compatible, I added the {\tt -ef} flag to the 
{\tt Linux\_cray.mak} file located in {\tt amrex/Tools/F\_mk/comps}. I also 
added a few more debugging flags:
\begin{lstlisting}[language=make,mathescape=false]
  FFLAGS   += -J $(mdir) -I $(mdir) -emf
  F90FLAGS += -J $(mdir) -I $(mdir) -emf

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\sf AMReX GMakedefs.mak} makefile}

In {\sf MAESTRO}, {\tt .mod} files are located in the {\tt \$(tdir)/m} 
directory, where {\tt tdir = t/\$(suf)} and {\tt \$(suf)} was in this case 
{\tt Linux.Cray}. This means the {\sf MAESTRO} routines are expecting to find 
module files with the name {\tt t/Linux.Cray/m/network.mod}. The addition of 
the {\tt -ef} flag affects the entire name of the module so the Cray compiler 
was creating files with the name {\tt t/linux.cray/m/network.mod}. To solve 
this, I modified what {\tt tdir} is defined to be when using the Cray compiler. 
This was done in the {\tt amrex/Tools/F\_mk/GMakedefs.mak} makefile by using 
a simple if statement:
\begin{lstlisting}[language=make,mathescape=false]
  ifeq ($(COMP), Cray)
    tdir = t/$(shell echo $(suf) | tr A-Z a-z)
  else
    tdir = t/$(suf)
  endif
  odir = $(tdir)/o
  mdir = $(tdir)/m
\end{lstlisting}
The shell command {\tt echo \$(suf) | tr A-Z a-z} has the effect of converting 
{\tt \$(suf)} to lowercase.

### 2018-11-07 Docs/makefiles/makefiles.tex

The main macros that define the build process are split across several
files.  The 4 main files are:
\begin{itemize}
\item {\tt \$\{AMREX\_HOME\}/Tools/F\_mk/GMakedefs.mak}:

@@

\item {\tt \$\{AMREX\_HOME\}/Tools/F\_mk/GMakeMPI.mak}:

@@

\item {\tt \$\{AMREX\_HOME\}/Tools/F\_mk/GMakerules.mak}:

@@

  This is a \maestro-specific file that gathers all of the various
  modules that are used to build a typical \maestro\ application
  and integrates with the \amrex\ build system.  Every \maestro\
  problem's {\tt GNUmakefile} will include this file.

@@

\maestro\ gets the location of the \amrex\ library through the 
{\tt AMREX\_HOME} variable.  This should be set as an environment
variable in your shell start-up files (e.g.\ {\tt .bashrc} or {\tt
.cshrc}).

The \amrex\ build system separates the compiler-specific information
from the machine-specific information---this allows for reuse of the
compiler information.  The only machine-specific parts of the build system
are for the MPI library locations, contained in {\tt GMakeMPI.mak}.
The compiler flags for the various compilers are listed in the
files in {\tt \$\{AMREX\_HOME\}/Tools/F\_mk/comps/}.  The compiler
is set via the {\tt COMP} variable in the problem's {\tt GNUmakefile}.

@@

The \amrex\ build system relies on the vpath functionality of {\tt
make}.  In a makefile, the {\tt vpath} variable holds search path used
to locate source files.  When a particular file is needed, the
directories listed in {\tt vpath} are searched until the file is
found.  The first instance of a file is used.  We exploit this feature
by always putting the build directory first in {\tt vpath} (this is
done in {\tt GMakerules.mak}).  This means that if a source file is
placed in the build directory, that copy will override any other
version in the source path.

@@

There is no need to explicitly define the dependencies between the
source files for Fortran modules.  The scripts in {\tt
AMREX\_HOME/Tools/F\_scripts/} are run at the start of the build
process and parse all the source files and make an explicit list of
the dependency pairs.  The execution of these scripts is triggered
by including makefiles of the form {\tt *.depends}.  On a fresh build these
will not exist.  When GNU make cannot find an included makefile it will
first attempt to build it using any relevant targets before issuing an 
error.  The targets for the {\tt *.depends} files contain the recipe for
executing the dependency scripts.  Once these makefiles are built by the
scripts GNU make will then read the dependencies for the current build
from them.  This process is defined in {\tt GMakerules.mak}.

@@

  This is the module that controls runtime parameters.  This is
  created by the script
  {\tt write\_probin.py} in {\tt \$\{AMREX\_HOME\}/Tools/F\_scripts/}.  The
  makefile logic for creating it is in {\tt GMaestro.mak}.  At compile
  time, the problem, main {\tt MAESTRO/}, and any microphysics
  directories (set from the {\tt EOS\_DIR}, {\tt CONDUCTIVITY\_DIR}, and {\tt NETWORK\_DIR} parameters in the {\tt GNUmakefile}
  are searched for {\tt \_parameter} files.  These files
  are parsed and the {\tt probin.f90} file is output containing the 
  runtime parameters, their default values, and the logic for reading
  and interpreting the inputs file.

@@

  This is a module that contains basic information about the build
  environment (compiler used, build machine, build directory, compiler
  flags, etc.).  This is created by the script {\tt makebuildinfo.py}
  in {\tt \$\{AMREX\_HOME\}/Tools/F\_scripts/} from {\tt
  GMaestro.mak} by passing in a number of makefile variables.  This is
  rewritten everytime the code is compiled.  The primary use of this
  module is writing out the {\tt job\_info} file in the plotfiles.

@@

Several modules are included in all \maestro\ builds by default.
From \amrex, we alway include:
\begin{itemize}
\item {\tt \$\{AMREX\_HOME\}/Src/F\_BaseLib}
\item {\tt \$\{AMREX\_HOME\}/Src/LinearSolvers/F\_MG}
\end{itemize}

@@

You can instead link in a system-wide optimized BLAS library by setting
{\tt SYSTEM\_BLAS := t}\otherindex{{\tt GNUmakefile}}{BLAS} in the {\tt GNUmakefile}.  This adds {\tt -lblas}
to the link line, and assumes that the library is in your path.  Note
that for some systems, you should have the static BLAS libraries 
available.

From {\tt MAESTRO/}, we add
\begin{itemize}
\item {\tt MAESTRO/constants}
\item {\tt MAESTRO/Source}
\end{itemize}
(although see the unit tests section below regarding {\tt MAESTRO/Source}.

@@

\subsection{\amrex-only Tests}

@@

\amrex\ has several options that produce executables that can help
track down memory issues, uninitialized variables, NaNs, etc.

@@

  Setting {\tt TEST := t}\otherindex{{\tt GNUmakefile}}{TEST} will
  enable routines in \amrex\ initialize multifabs and arrays 
  allowed via {\tt bl\_allocate} to signalliing NaNs.  This behavior
  is the same as {\tt NDEBUG :=}, but {\tt TEST := t} uses the 
  same compiler optimizations as a normal build.

  This can be useful with compiler flags that trap floating point
  exceptions (FPEs), but checks on floating point exceptions can also
  be enabled through runtime parameters passed to \amrex's
  backtrace functionlity:
  \begin{itemize}
  \item \runparam{boxlib\_fpe\_invalid}: enabling FPE trapping for
    invalid operations (e.g. {\tt 0 * inf}, {\tt sqrt(-1)})

@@

  When exception trapping is enabled (either via \amrex\ or the
  compiler), the code will abort, and the backtrace information will
  be output to a file {\tt Backtrace.N}, where {\tt N} is the
  processor number.  \amrex\ will also initialize \multifab s with
  signaliing NaNs to help uncover any floating point issues.

@@

  Behind the scenes, \amrex\ implements this capability via the
  Linux/Unix {\tt feenableexcept} function (this is in {\tt
    backtrace\_c.cpp} in \amrex).

@@

Properties for different compilers are already defined in {\tt
  \$\{AMREX\_HOME\}/Tools/F\_mk/comps/}.  Each compiler is given its
own file.  The appropriate file is included into {\tt GMakedefs.mak}
by looking at the {\tt COMP} variable and the operating system.  These
compiler files define the compiler flags for both optimized and debug
compiling.  Additionally, the variable {\tt FCOMP\_VERSION} should be
defined there, based on the output from the compiler, to provide the
compiler version for output into the {\tt job\_info} file at runtime.

>>>>

The main macros that define the build process are split across several
files.  The 4 main files are:
\begin{itemize}
\item {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_mk/GMakedefs.mak}:

@@

\item {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_mk/GMakeMPI.mak}:

@@

\item {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_mk/GMakerules.mak}:

@@

  This is a \maestro-specific file that gathers all of the various
  modules that are used to build a typical \maestro\ application
  and integrates with the \fboxlib\ build system.  Every \maestro\
  problem's {\tt GNUmakefile} will include this file.

@@

\maestro\ gets the location of the \fboxlib\ library through the 
{\tt FBOXLIB\_HOME} variable.  This should be set as an environment
variable in your shell start-up files (e.g.\ {\tt .bashrc} or {\tt
.cshrc}).

The \fboxlib\ build system separates the compiler-specific information
from the machine-specific information---this allows for reuse of the
compiler information.  The only machine-specific parts of the build system
are for the MPI library locations, contained in {\tt GMakeMPI.mak}.
The compiler flags for the various compilers are listed in the
files in {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_mk/comps/}.  The compiler
is set via the {\tt COMP} variable in the problem's {\tt GNUmakefile}.

@@

The \fboxlib\ build system relies on the vpath functionality of {\tt
make}.  In a makefile, the {\tt vpath} variable holds search path used
to locate source files.  When a particular file is needed, the
directories listed in {\tt vpath} are searched until the file is
found.  The first instance of a file is used.  We exploit this feature
by always putting the build directory first in {\tt vpath} (this is
done in {\tt GMakerules.mak}).  This means that if a source file is
placed in the build directory, that copy will override any other
version in the source path.

@@

There is no need to explicitly define the dependencies between the
source files for Fortran modules.  The scripts in {\tt
FBOXLIB\_HOME/Tools/F\_scripts/} are run at the start of the build
process and parse all the source files and make an explicit list of
the dependency pairs.  The execution of these scripts is triggered
by including makefiles of the form {\tt *.depends}.  On a fresh build these
will not exist.  When GNU make cannot find an included makefile it will
first attempt to build it using any relevant targets before issuing an 
error.  The targets for the {\tt *.depends} files contain the recipe for
executing the dependency scripts.  Once these makefiles are built by the
scripts GNU make will then read the dependencies for the current build
from them.  This process is defined in {\tt GMakerules.mak}.

@@

  This is the module that controls runtime parameters.  This is
  created by the script
  {\tt write\_probin.py} in {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_scripts/}.  The
  makefile logic for creating it is in {\tt GMaestro.mak}.  At compile
  time, the problem, main {\tt MAESTRO/}, and any microphysics
  directories (set from the {\tt EOS\_DIR}, {\tt CONDUCTIVITY\_DIR}, and {\tt NETWORK\_DIR} parameters in the {\tt GNUmakefile}
  are searched for {\tt \_parameter} files.  These files
  are parsed and the {\tt probin.f90} file is output containing the 
  runtime parameters, their default values, and the logic for reading
  and interpreting the inputs file.

@@

  This is a module that contains basic information about the build
  environment (compiler used, build machine, build directory, compiler
  flags, etc.).  This is created by the script {\tt makebuildinfo.py}
  in {\tt \$\{FBOXLIB\_HOME\}/Tools/F\_scripts/} from {\tt
  GMaestro.mak} by passing in a number of makefile variables.  This is
  rewritten everytime the code is compiled.  The primary use of this
  module is writing out the {\tt job\_info} file in the plotfiles.

@@

Several modules are included in all \maestro\ builds by default.
From \fboxlib, we alway include:
\begin{itemize}
\item {\tt \$\{FBOXLIB\_HOME\}/Src/F\_BaseLib}
\item {\tt \$\{FBOXLIB\_HOME\}/Src/LinearSolvers/F\_MG}
\end{itemize}

@@

You can instead link in a system-wide optimized BLAS library by setting
{\tt SYSTEM\_BLAS := t}\otherindex{{\tt GNUmakefile}}{BLAS} in the {\tt GNUmakefile}.  This will
use the library specified in \otherindex{{\tt GNUmakefile}}{BLAS\_LIBRARY} {\tt BLAS\_LIBRARY}
(defaulting to {\tt -lopenblas})
to the link line, and assumes that the library is in your path.  Note
that for some systems, you should have the static BLAS libraries 
available.

From {\tt MAESTRO/}, we add
\begin{itemize}
\item {\tt MAESTRO/constants}
\item {\tt MAESTRO/Source}
\end{itemize}
(although see the unit tests section below regarding {\tt MAESTRO/Source}.)

@@

\subsection{\fboxlib-only Tests}

@@

\fboxlib\ has several options that produce executables that can help
track down memory issues, uninitialized variables, NaNs, etc.

@@

  Setting {\tt TEST := t}\otherindex{{\tt GNUmakefile}}{TEST} will
  enable routines in \fboxlib\ initialize multifabs and arrays 
  allowed via {\tt bl\_allocate} to signalliing NaNs.  This behavior
  is the same as {\tt NDEBUG :=}, but {\tt TEST := t} uses the 
  same compiler optimizations as a normal build.

  This can be useful with compiler flags that trap floating point
  exceptions (FPEs), but checks on floating point exceptions can also
  be enabled through runtime parameters passed to \fboxlib's
  backtrace functionlity:
  \begin{itemize}
  \item \runparam{boxlib\_fpe\_invalid}: enabling FPE trapping for
    invalid operations (e.g. {\tt 0 * inf}, {\tt sqrt(-1)})

@@

  When exception trapping is enabled (either via \fboxlib\ or the
  compiler), the code will abort, and the backtrace information will
  be output to a file {\tt Backtrace.N}, where {\tt N} is the
  processor number.  \fboxlib\ will also initialize \multifab s with
  signaliing NaNs to help uncover any floating point issues.

@@

  Behind the scenes, \fboxlib\ implements this capability via the
  Linux/Unix {\tt feenableexcept} function (this is in {\tt
    backtrace\_c.cpp} in \fboxlib).

@@

Properties for different compilers are already defined in {\tt
  \$\{FBOXLIB\_HOME\}/Tools/F\_mk/comps/}.  Each compiler is given its
own file.  The appropriate file is included into {\tt GMakedefs.mak}
by looking at the {\tt COMP} variable and the operating system.  These
compiler files define the compiler flags for both optimized and debug
compiling.  Additionally, the variable {\tt FCOMP\_VERSION} should be
defined there, based on the output from the compiler, to provide the
compiler version for output into the {\tt job\_info} file at runtime.

### 2018-11-07 Docs/visualization/visualization.tex

\subsection{the \boxlib\ file format}

@@

\amrvis\ is a tool developed together with \boxlib\ to visualize datasets
from codes built around the \boxlib\ library.  You can download the
\amrvis\ source from: \\
\url{https://ccse.lbl.gov/Downloads/downloadAmrvis.html} \\

\amrvis\ exists in the C++ \boxlib\ framework, so the build system is
slightly different.  A different executable is needed for 2- vs.\ 3-d
datasets.  Edit the {\tt GNUmakefile} and set the compilers (probably
{\tt g++} and {\tt gfortran}) and the dimensionality, and turn off any
of the volume rendering options.  You will need to have the Motif library
installed on your system (or a replacement, such as {\tt lesstif}.

@@

{\tt AmrPostprocessing/python} provides some simple commandline
tools for doing visualizations of \boxlib\ plotfiles (note: a subset
of these are distributed directly with \boxlib\ in {\tt BoxLib/Tools/Py\_util/}).  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

@@

{\tt plotsinglevar.py} does visualizations of 2-d \boxlib\ plotfiles,
and slices through 3-d \boxlib\ plotfiles.  A simple plot can be made
via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``{\tt tfromp}'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

\yt is a Python package for analyzing and visualizing simulation data.
Originally \yt was written for the {\tt Enzo} code, with focus on
cosmological simulation data.  It has since been refactored to remove
the specific {\tt Enzo}isms, and now can work on various data formats,
such as the BoxLib data from \maestro\ and \castro, HDF5 data
from {\tt FLASH}, and data from the SPH code {\tt Gadget}.  For more
information, see the \yt homepage at \url{http://yt-project.org/} and
\cite{yt}.

>>>>

\subsection{the \amrex\ file format}

@@

\amrvis\ is a tool developed together with \amrex\ to visualize
datasets from codes built around the \amrex\ library (including
\fboxlib\ used here).  You can download the \amrvis\ source from:
\\ \url{https://ccse.lbl.gov/Downloads/downloadAmrvis.html} \\

\amrvis\ exists in the C++ \amrex\ framework, so the build system is
slightly different.  A different executable is needed for 2- vs.\ 3-d
datasets.  Edit the {\tt GNUmakefile} and set the compilers (probably
{\tt g++} and {\tt gfortran}) and the dimensionality, and turn off any
of the volume rendering options.  You will need to have the Motif library
installed on your system (or a replacement, such as {\tt lesstif}.

@@

{\tt AmrPostprocessing/python} provides some simple commandline
tools for doing visualizations of \amrex\ plotfiles (note: a subset
of these are distributed directly with \amrex\ in {\tt amrex/Tools/Py\_util/}).  The main drivers
are written in python and use a set of Fortran routines, compiled with
{\tt f2py} to interface with the plotfile data.  To use the routine,
you will need to have {\tt matplotlib} and {\tt f2py} installed.  On a
machine running Fedora linux, you can install these packages via
\begin{verbatim}   
yum install python-matplotlib f2py
\end{verbatim}
%
The library required by the python routines can be built by typing
'{\tt make}' in that directory.  If successful, you should find
a library {\tt fsnapshot.so}.

@@

{\tt plotsinglevar.py} does visualizations of 2-d \amrex\ plotfiles,
and slices through 3-d \amrex\ plotfiles.  A simple plot can be made
via:
\begin{verbatim}
plotsinglevar.py --log -o test.png plt00000/ tfromp
\end{verbatim}
This will make a plot of ``{\tt tfromp}'' from the plotfile {\tt plt00000} with log scaling,
and store the output in {\tt test.png}.  See Figure~\ref{fig:python}.
If you don't do `{\tt -o}', then a default output filename consisting of the
plotfile name + component will be used.

@@

\yt is a Python package for analyzing and visualizing simulation data,
and understand that \amrex\ data from \maestro\ and \castro\ (along
with many other simulation codes). For more
information, see the \yt homepage at \url{http://yt-project.org/} and
\cite{yt}.
